---
title: "p8105_Hw1_asn2139"
author: "Akanksha Nalatwad"
date: 2019-09-16
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

Create a data frame comprised of 

1) a random sample of size 10 from a standard normal distribution


```{r}
samp= rnorm (10)
length= samp
```
2) a logical vector indicating whether elements of the sample are greater than 0

```{r}
samp >0
```

3) a character vector of length 10

```{r}
y= "characters"
```

4)a factor vector of length 10, with 3 different factor “levels”

```{r}
funthings = factor(c("happy", "sad", "angry"))
class(funthings)
levels (funthings)
```
```{r}
mean(samp)
mean (y)
mean (funthings)
```



Second code chunk

convert the logical vector to numeric, and multiply the random sample by the result
```{r}
as.numeric(y)*samp
```
convert the logical vector to a factor, and multiply the random sample by the result
```{r}
factor(y)*samp
```
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
factor(y)
as.numeric(factor(y))*samp
```

# Problem 2



```{r}
data("penguins", package = "palmerpenguins")
penguins
summary(penguins)
nrow(penguins)*ncol(penguins)

ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm))
```



